
---
title: "Using the xkcd package"
vignette: >
  %\VignetteIndexEntry{Using the xkcd package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

```{r setup}
library(xkcd)
```

## Browsing xkcd comics 

The main function of the xkcd package is to let you browse xkcd comics from with in R. Let's see how we can accomplish this. First, load the `xkcd` package.

Then, use the `xkcd()` function to retrieve information about a particular comics. We'll retrieve information about the very first xkcd comics, so we'll set the `number` argument equal to 1.

```{r}
first_comic <- xkcd(number = 1)
print(first_comic)
```

The `draw_comic()` function takes in this list of metadata, and displays the actual comic strip image in the plot window:
```{r}
draw_comic(first_comic)
```

## Comic Data
The xkcd package also comes with a built-in data set describing the first 10 xkcd comics ever published

```{r}
xkcd::xkcd_comics
```
